Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-07-21 vita.tex
fix broken vita markup
added some more data to vita

\begin{tabular}{@{\hspace{0.2in}}@{\hspace{0.2in}}p{4.5in}}

{NAME:}
& Joel Adam Berger \\
\\
{EDUCATION:}
& B.S., Physics, University of Illinois at Chicago,\\
& Chicago, Illinois, 2005 \\
\\
{\Large TEACHING:}
& Something here\\

\end{tabular}

>>>>

%\begin{tabular}{@{\hspace{0.2in}}@{\hspace{0.2in}}p{4.5in}}
\begin{tabular}{p{1.5in}p{6in}}
NAME: & Joel Adam Berger \\
\\
EDUCATION: & B.S., Physics, University of Illinois at Chicago,\\
& Chicago, Illinois, 2005 \\
\\
TEACHING: & Something here\\
\\
PROFESSIONAL MEMBERSHIPS: & Microscopy Society of America\\
& Midwest Microscopy and Microanalysis Society\\
\\
SELECTED \nobreak{PUBLICATIONS:} &\\
\end{tabular}
